Normalized expressions

### 2021-02-26 analysis/normalized.Rmd
More on parse and plot pattern
Improve

@@

```{r}
big_topcall %>% datatable()
```

@@

@@

```{r}
stat_functions <- c("model.frame", "glm", "plm", "elo.model.frame", "lmer", "randomForest", "betareg", "nlreg", "model.frame.default", "model.matrix", "arima", "glm.nb", "glmer") # There are many more

@@

```{r}
plotting <- E_cano %>% filter(str_detect(topcall, fixed("plot")))

>>>>

```{r}
widespread_topcall %>% datatable()
```

@@

@@

Is the `envir` argument non trivial?

```{r}
assign_env <- assigns %>% filter(!is.na(envir))

nb_a_env_call_sites <- assign_env %>% pull(src_ref) %>% n_distinct()
```

There are `r nb_a_env_call_sites` call sites where `envir` is non-trivial, with an assignment.

@@

```{r}
stat_functions <- c("model.frame", "glm", "lm", "plm", "elo.model.frame", "lmer", "randomForest", "betareg", "nlreg", "model.frame.default", "model.matrix", "arima", "glm.nb", "glmer") # There are many more

@@

```{r}
plotting <- E_cano %>% filter(str_detect(normalized, fixed("plot"))) # not in topcall because f it results from parse...
